The Skew-Normal Approximation of the Binomial Distribution

### 2011-02-08 project/paper/accuracy.tex
Made some minor changes, as requested by second reader.

The first and most obvious way of judging accuracy is by visual inspection.
Figures \ref{fig:comparison-n25}, \ref{fig:comparison-n50}, and
\ref{fig:comparison-n100} in appendix \ref{app:figures} compare the binomial,
normal, and skew-normal at small values of $p$ for $n=25$, $n=50$, and $n=100$,
respectively.

The graphs show that at moderate $n$ and small $p$, our skew-normal curve
follows the shape of the binomial much more closely than the normal. As $n$
grows, however, the Central Limit Theorem begins to exert its effect and the
normal distribution "catches up" in accuracy. Thus as we would expect, the
skew-normal approximation is of greatest value in the former set of cases.

>>>>

The first and most obvious way of judging accuracy is by visual inspection.
Figures \ref{fig:comparison-n25}, \ref{fig:comparison-n50}, and
\ref{fig:comparison-n100} in appendix \ref{app:figures} compare the binomial,
normal, and skew-normal at the small values of $p=0.05$, $p=0.1$, and $p=0.2$
for $n=25$, $n=50$, and $n=100$, respectively.

The graphs in figures \ref{fig:comparison-n25}, \ref{fig:comparison-n50}, and
\ref{fig:comparison-n100} indicate that at moderate $n$ and small $p$, our
skew-normal curve follows the shape of the binomial much more closely than the
normal. As $n$ grows for each value of $p$, however, the Central Limit Theorem
begins to exert its effect and the normal distribution "catches up" in
accuracy, slowly for for more extreme values of $p$ and faster as $p$
approaches 0.5. Thus as we would expect, the skew-normal approximation is of
greatest value when $n$ is moderate and $p$ is extreme.
